### 2019-08-30 reports/thesis/chapters/2_dataCollection.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section
Revise thesis and qq plot for compound poisson

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing between the source and the detector with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\cdots, W$ and $y=1,2,3,\cdots,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.

@@

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\cdots,n$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{n}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

@@

Linear shading correction performed well, in terms of ANOVA, on all greyscale projections except for the black image. This is because linear shading correction trains on greyscale projections of various powers and generalises to these powers. Linear shading correction is used throughout this thesis.

>>>>

Greyscale projections were taken for calibration \citep{wang2008experimental} in addition to the projection of the test object. These are projections with nothing between the source and the detector with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively.

@@

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,n$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{n}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

@@

Linear shading correction outperformed BW shading correction, in terms of ANOVA, on all greyscale projections except for the black image. This is because linear shading correction trains on greyscale projections of various powers and generalises to these powers. Linear shading correction is used throughout this thesis.

### 2019-08-30 reports/thesis/chapters/5_inference.tex
Revise thesis and qq plot for compound poisson

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and is used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

@@

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics. Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}.

@@

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

>>>>

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice \citep{wasserstein2019moving} and is used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

@@

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics. Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}. Lastly, because the titanium test sample was created using a power-based method, the voids may be filled with power thus appear with less contrast in the projections making it hard to detect.

@@

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null. However, numerical methods are still required to find the mode. Exact solutions for the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.

The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
